Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/relwk.tex
Add PADS citation

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{back2002datascript}.
A broader overview of data
description languages can be found in~\cite{Fisher:700DDL}. However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. However, these systems cannot handle complicated encodings such as compressed data, which
are supported by Nail's stream transforms. Many built-in features of these date description
languages, such as the various ways of encoding array size or length and offsets, can be expressed
by Nail transformations, keeping the core language itself smaller and increasing flexibility.

Parser generators for binary protocols were first introduced by the
Hammer~\cite{hammer-parser} parser.
While previous parser generators could also be used to write grammars
for binary protocols,\footnote{Theoretically speaking, the alphabet
over which a grammar is an abstract set, so most algorithms work
just as well on an alphabet of $\{0,1\}$.} doing so is practically
inconvenient. Hammer allows the programmer to specify a grammar in
terms of bits and bytes instead of characters. Common concerns, such as
endianness and bit-packing, are handled transparently.

Hammer implements grammars as language-integrated parser combinators, an approach popularized by
Parsec for Haskell~\cite{LeijenMeijer:parsec}. The parser combinator style (to our knowledge, first
described by Burge~\cite{burge1975recursive}) is a natural way of concisely expressing top-down
grammars~\cite{Danielsson:2010:TPC:1863543.1863585}
by composing them from one or multiple sub-parsers.\footnote{For more
background on the history of expressing grammars, see Bryan Ford's
masters thesis~\cite{ford2002packrat}, which also describes the
default parsing algorithm used by Hammer.}
Hammer then constructs a tree of function pointers which can be invoked to parse a given input into
an AST\@.

>>>>

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{back2002datascript}. 
A broader overview of data
description languages can be found in~\cite{Fisher:700DDL}. However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. A
particularly sophisticated data description language, PADS~\cite{Fisher:2005:PDL:1064978.1065046},
which is targeted more towards offline analysis, even features built-in support for XML and
automatic grammar inference.

However, these systems cannot easily handle complicated encodings such as compressed data, which are
supported by Nail's stream transforms. While sophisticated languages like PADS allow for handling
particular variations of offset fields, compressed data or even XML entities, each of these
features has to be implemented in the data description language - and all associated tools. Nail's
transformations keep the core language practicably small, while enabling the wide range of
features real-world protocols require.

Recently, the Hammer project~\cite{hammer-parser} introduced a security-focused parser framework for
binary protocols.
Hammer implements grammars as language-integrated parser combinators, an approach popularized by
Parsec for Haskell~\cite{LeijenMeijer:parsec}. The parser combinator style (to our knowledge, first
described by Burge~\cite{burge1975recursive}) is a natural way of concisely expressing top-down
grammars~\cite{Danielsson:2010:TPC:1863543.1863585}
by composing them from one or multiple sub-parsers.\footnote{For more
background on the history of expressing grammars, see Bryan Ford's
masters thesis~\cite{ford2002packrat}, which also describes the
default parsing algorithm used by Hammer.}
Hammer then constructs a tree of function pointers which can be invoked to parse a given input into
an AST\@.
